---
title: "Week 3 Part 2 Functions"
author: "verdap01"
date: "2024-01-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The function remind_me() takes no arguments. When used it will return a list of things
I need to remember this week. This list is attached to variable to_do, which is
returned in the function.


```{r remind_me}
knitr::opts_chunk$set(echo = TRUE)

remind_me <- function() {
  to_do <-
    c(
      "Finish R assignment due Friday",
      "Buy fairy lights for friend's birthday on Monday",
      "Help friend move on Wednesday",
      "Rewatch R lectures for exam next Friday"
    )
  return(to_do)
}
```



The following function cheat() is used to return the answers to questions 1, 2 or
3 in assignment 3.2. The function takes one argument.

If the input to the function (question) is 1, the if statement will run and print
the answer code for the first question. The answers to question 2 and 3 will be
displayed if question == 2 or question == 3 due to the elseif statements:

```{r cheat function}
knitr::opts_chunk$set(echo = TRUE)

cheat <- function(question) {
  if (question == 1) {
    print("set.seed(14857642)")
    print("exam_grades <- trunc(rnorm(70, mean = 6, sd = 2))")
    print(
      "hist(exam_grades, col = 'lightgreen', main = 'Histogram of Exam Grades',xlab = 'Grades', ylab = 'Frequency of Students')"
    )
  } else if (question == 2) {
    print("schipholdata <-read.csv('/path/to/file/schiphol_data.csv')")
    print(
      "plot(schipholdata$DATE, schipholdata$TMIN, type = 'p', main = 'Minimum Temperatures Recorded at Schiphol Airport Between 1951-2021', xlab = 'Time', ylab = 'Temperature')"
    )
  } else if (question == 3) {
    print("install.packages('titanic')")
    print("library('titanic')")
    print("t_gender <- titanic_train$Sex")
    print(
      "t_alive <- factor(titanic_train$Survived, levels = c(0, 1), labels = c('dead', 'alive'))"
    )
    print("titanicdata <- data.frame(t_gender, t_alive)")
    print(
      "ggplot(titanicdata, aes(x = t_gender, fill = t_alive)) + geom_bar(position = 'stack') + labs(x = 'sex', y = 'count', fill = 'How did it go?')"
    )
  } else
    print("Question number must be 1, 2 or 3")
}
```

If the function input is not 1,2 or 3, the function will print a message conveying
this (the final else statement).





The following function creates concentric squares with randomized colors. First
"dplyr" is loaded using the library function. Then, the make_art function is defined.
The function will take one argument "seed" which is used to set seed and obtain 
the same randomisation each time.

Next, a function random_color is defined which generates a random color; the 
function does not need any input arguments. 

Next, the coordinates of a square are created and placed in a tibble so that it
may be plotted later on.

The squares are plotted using ggplot() + geom_polygon functions, which are filled
with the random_color() function generated earlier. For each geom_polygon function
rendered, the dimensions of the square are reduced 5 units by making the appropriate
alterations in the x and y variables defined bove, which make up the coordinates.

```{r make_art function}
knitr::opts_chunk$set(echo = TRUE)

library("dplyr")
library("tidyverse")

make_art <- function(seed) {
  set.seed(seed)

  random_color <- function() {
    rgb(runif(1), runif(1), runif(1)) #Colors are between 0-1 which is the runif() default
  }

  x = c(1, 150, 150, 1) #variable name "x" as this represents the x-coordinates when plotted
  y = c(1, 1, 150, 150) #variable name "y" as this represents the y-coordinates when plotted
  square = tibble(x = x, y = y)

   ggplot() +
    geom_polygon(
      data = square,
      aes(x = x, y = y),
      fill = random_color(),
    ) +
    geom_polygon(data = square, aes(x = c((x[1] + 5), (x[2] - 5), (x[3] -
                                                                     5), (x[4] + 5)), y = c((y[1] + 5), (y[2] + 5), (y[3] - 5), (y[4] - 5))), fill =
                   random_color()) +
    geom_polygon(data = square, aes(x = c((x[1] + 10), (x[2] - 10), (x[3] -
                                                                       10), (x[4] + 10)), y = c((y[1] + 10), (y[2] + 10), (y[3] - 10), (y[4] -
                                                                                                                                          10))), fill = random_color()) +
    geom_polygon(data = square, aes(x = c((x[1] + 15), (x[2] - 15), (x[3] -
                                                                       15), (x[4] + 15)), y = c((y[1] + 15), (y[2] + 15), (y[3] - 15), (y[4] -
                                                                                                                                          15))), fill = random_color()) +
    geom_polygon(data = square, aes(x = c((x[1] + 20), (x[2] - 20), (x[3] -
                                                                       20), (x[4] + 20)), y = c((y[1] + 20), (y[2] + 20), (y[3] - 20), (y[4] -
                                                                                                                                          20))), fill = random_color()) +
    geom_polygon(data = square, aes(x = c((x[1] + 25), (x[2] - 25), (x[3] -
                                                                       25), (x[4] + 25)), y = c((y[1] + 25), (y[2] + 25), (y[3] - 25), (y[4] -
                                                                                                                                          25))), fill = random_color()) +
    geom_polygon(data = square, aes(x = c((x[1] + 30), (x[2] - 30), (x[3] -
                                                                       30), (x[4] + 30)), y = c((y[1] + 30), (y[2] + 30), (y[3] - 30), (y[4] -
                                                                                                                                          30))), fill = random_color()) +
    geom_polygon(data = square, aes(x = c((x[1] + 35), (x[2] - 35), (x[3] -
                                                                       35), (x[4] + 35)), y = c((y[1] + 35), (y[2] + 35), (y[3] - 35), (y[4] -
                                                                                                                                          35))), fill = random_color()) +
    geom_polygon(data = square, aes(x = c((x[1] + 40), (x[2] - 40), (x[3] -
                                                                       40), (x[4] + 40)), y = c((y[1] + 40), (y[2] + 40), (y[3] - 40), (y[4] -
                                                                                                                                          40))), fill = random_color()) +
    geom_polygon(data = square, aes(x = c((x[1] + 45), (x[2] - 45), (x[3] -
                                                                       45), (x[4] + 45)), y = c((y[1] + 45), (y[2] + 45), (y[3] - 45), (y[4] -
                                                                                                                                          45))), fill = random_color()) +
    geom_polygon(data = square, aes(x = c((x[1] + 50), (x[2] - 50), (x[3] -
                                                                       50), (x[4] + 50)), y = c((y[1] + 50), (y[2] + 50), (y[3] - 50), (y[4] -
                                                                                                                                          50))), fill = random_color())
  
}
```


